Towards In-Switch Reinforcement Learning

### 2020-12-02 interim-talk/talk.tex
Talk!

\documentclass[aspectratio=169,xcolor={dvipsnames}
%,notes=only
%,notes
%,show notes on second screen=right
,handout
]{beamer}
\usetheme[background=light, numbering=fraction]{metropolis}
\usepackage{appendixnumberbeamer}
\usepackage{pgfpages}

@@

\usepackage{lipsum}
\usepackage[basic]{complexity}
\usepackage[super,negative]{nth}

@@

%bib
\usepackage[maxnames=3,maxbibnames=99,mincrossrefs=5,sortcites
,backend=bibtex
,style=authortitle
]{biblatex}
%\addbibresource{papers.bib}
%\addbibresource{confs-journs.bib}

@@

\title{Reinforcement Learning in Future Networks}
\author{\vspace{-1em}\textbf{Kyle A. Simpson}\\
	\faEnvelopeO{} \href{mailto:k.simpson.1@research.gla.ac.uk}{\nolinkurl{k.simpson.1@research.gla.ac.uk}}\\
	\vspace{1em}\small{\faGithub{} \href{https://github.com/felixmcfelix}{FelixMcFelix} \hspace{0.5em} \faGlobe{} \url{https://mcfelix.me}}}
\institute{University of Glasgow}
\date{\nth{27} March, 2020}

@@

\begin{frame}{Data-driven networking: DDoS Prevention}
	\begin{columns}
		\begin{column}{0.6\linewidth}
			\begin{figure}
				\centering
				\resizebox{\linewidth}{!}{
					\begin{tikzpicture}[
					texts/.style = {text=black},
					labeltexts/.style = {text=gray},
					treeline/.style = {draw=uofgburgundy},
					treenode/.style = {texts, circle, centered, fill=white, treeline},
					load/.style = {fill=uofgcobalt},
					loadline/.style = {draw=uofgcobalt, line width=0.75mm},
					loadhide/.style = {fill=uofgcobalt!40!white},
					external/.style = {fill=uofgrust},
					externalhide/.style = {fill=uofgrust!40!white},
					hideline/.style = {draw=uofgsandstone!40!white},
					hidenode/.style = {treenode, hideline},
					grow'=right
					]
					\node [treenode, loadhide, label={[texts]above:Agent 1}] (mainagent) {};
					\node [treenode, loadhide, right = of mainagent] (inner0) {};
					\node [treenode, loadhide, above right = 0.2cm and 1cm of inner0] (inner1) {};
					\node [hidenode, below right = 0.2cm and 1cm of inner0] (inner2) {};
					\node [treenode, loadhide, below right = 0.2cm and 1cm of inner1] (inner3) {};
					\node [treenode, loadhide, right = of inner3] (inner4) {};
					\node [treenode, loadhide, above right = 0.2cm and 1cm of inner4, label={[texts]above:$s_0$}] (s0) {};
					\node [hidenode, below right = 0.2cm and 1cm of inner4, label={[labeltexts]above:$s_1$}] (s1) {};

					\end{tikzpicture}
				}
			\caption{`Global' state for any flow (\textbf{bold} means used by policy).}
			\end{figure}
		\end{column}
		\begin{column}{0.4\linewidth}
			\begin{itemize}
				\item Monitor flow statistics at ingress/egress points.
				\item Use load measurements from flow paths as global state.
				\item OUTPUT: throttle individual flows.
			\end{itemize}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}{Data-driven networking: DDoS Prevention}
	\begin{columns}
		\begin{column}{0.3\linewidth}
			How does this perform compared to state of the art, SPIFFY...?
			\begin{itemize}
				\item Worse for congestion-aware, but strong.
				\item \alert{Improvement on VoIP/UDP traffic!}
				\item Learning time on order of minutes.
				\begin{itemize}
					\item Classical RL.
				\end{itemize}
			\end{itemize}
		\end{column}
		\begin{column}{0.7\linewidth}
			\begin{figure}
				\centering
				\includegraphics[width=0.75\linewidth]{tnsm-tcp-16-single}
				\caption{
					Online performance of RL agents for TCP traffic, with and without policy sharing.
					\label{fig:tcp-tree-16}
				}
			\end{figure}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}{Programmable data-planes: Motivation}
\begin{columns}
	\begin{column}{0.6\linewidth}
		\begin{figure}
			\resizebox{\linewidth}{!}{
			\begin{tikzpicture}
			\node (iLabel) {Theory};

@@

					\draw[dotted, ->, bend left = 30] (state) -- (agent) node[midway, above] {$t_1$};
					\draw[->] (agent) -- (action) node[midway, right] {$t_2$};
					\draw[dotted, ->] (action) -- (state') node[midway, below] {$t_3$};
					\end{tikzpicture}}};
			\end{tikzpicture}
			}
			\caption{Asynchronous RL delays and state slippage (policy updates omitted).}
		\end{figure}
	\end{column}
	\begin{column}{0.4\linewidth}
		\begin{itemize}
			\item Programmable network hardware: arbitrary in-network compute.
			\item In data-driven, want to \alert{minimise time to act}.
			\item RL assumes that action \& policy update are zero-cost.
			\begin{itemize}
				\item Not so in real deployments!
				\item State drift, etc.
			\end{itemize}
		\end{itemize}
	\end{column}
\end{columns}
\end{frame}

\begin{frame}{DDoS Prevention: VNF + SDN  architecture}
	\begin{columns}
%		\begin{column}{0.3\linewidth}
%			\begin{itemize}
%				\item Monitor flow statistics at ingress/egress points.
%				\item Use load measurements from flow paths as global state.
%				\item OUTPUT: throttle individual flows.
%			\end{itemize}
%		\end{column}
		\begin{column}{1.0\linewidth}
			\begin{figure}
				\centering
				\resizebox{0.7\linewidth}{!}{\begin{tikzpicture}[scale=1, every node/.style={scale=0.7}]
					\node(remote){Remote};

@@

					\draw[thick, ->] (avfsa.east) to [out=0, in=45] (avfrl.north);
					\node[right=0.3] at (avfsa.east) {\tiny Experience};
					\end{tikzpicture}}
				\caption{
					System architecture for RL-driven DDoS defence.
					\label{fig:sys-arch}
				}
				\vspace{-1em}
			\end{figure}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}{Programmable data-planes: An Architecture for RL}
\begin{columns}
	\begin{column}{0.6\linewidth}
		\begin{figure}
			\resizebox{1.2\linewidth}{!}{\begin{tikzpicture}
				\node[fill=white!80!uofgcobalt, draw=black, minimum height=1cm, minimum width=2.9cm, below right= 0.1 of sw2.north west](p4-master){};
				\node[below right, inner sep=2pt] at (p4-master.north west) {\small P4 Master Island};
				\node[fill=white!90!uofgcobalt, draw, rectangle, rounded corners=0.05cm, above=0.1] (p4-rules) at (p4-master.south) {\begin{varwidth}{2.5 cm}\scriptsize \centering Flow Control Rules\end{varwidth}};

				\node[fill=white!80!uofgcobalt, draw=black, minimum height=2cm, minimum width=2cm, below = 0.1 of p4-master](sw1){};
				\node[fill=white!80!uofgcobalt, draw=black, minimum height=2cm, minimum width=2cm, below right= 0.1 of sw1.north west](sw2){};
				\node[fill=white!80!uofgcobalt, draw=black, minimum height=2cm, minimum width=2cm, below right= 0.1 of sw2.north west](switch){};
				\node[below right, inner sep=2pt] at (switch.north west) {\small P4 Island};
				\node[fill=white!90!uofgcobalt, draw, rectangle, rounded corners=0.05cm, above=0.1] (oswlc) at (switch.south) {\begin{varwidth}{1.5 cm}\scriptsize \centering Control Packet Match\end{varwidth}};

				\node[fill=white!80!uofgcobalt, draw=black, minimum height=2cm, minimum width=2.9cm, below= 0.1 of switch](others){};
				\node[below right, inner sep=2pt] at (others.north west) {\small Other Islands};
				\node[fill=white!90!uofgcobalt, draw, rectangle, rounded corners=0.05cm, above=0.1] (others-etc) at (others.south) {\begin{varwidth}{2.5 cm}\scriptsize \centering \textellipsis \end{varwidth}};
				\node[fill=white!90!uofgcobalt, draw, rectangle, rounded corners=0.05cm, above=0.1] (others-int) at (others-etc.north) {\begin{varwidth}{2.5 cm}\scriptsize \centering In-band Network Telemetry\end{varwidth}};

				\node[fill=white!80!uofgsunshine, draw=black, minimum height=5cm, minimum width=5cm](rli) at ($(p4-master.east) + (3, -2)$){};
				\node[below right, inner sep=2pt] at (rli.north west) (rli-text) {\small RL Island};

				\node[draw=black, dotted, minimum height=1cm, minimum width=2cm](wq-out) at ($(rli-text.south) + (0.5,-0.5)$){};
				\node[below right, inner sep=2pt] at (wq-out.north west) {\small CLS};
				\node[fill=white!90!uofgsunshine, draw, rectangle, rounded corners=0.05cm, above=0.1] (wq-in) at (wq-out.south) {\begin{varwidth}{2.5 cm}\scriptsize \centering Work Queue\end{varwidth}};

@@

@@

				\draw[->] (p4-rules.west)  to [out=180,in=180,looseness=2]  node[pos=0.5, rotate=90, anchor=center, above] {Rules}(sw1);
				\draw[->] (p4-rules.west)  to [out=180,in=180,looseness=2] (sw2);
				\draw[->] (p4-rules.west)  to [out=180,in=180,looseness=2] (switch);

				\draw[->] (oswlc.east)  to node[midway, above, sloped] {\tiny Control, Requests} (wq-in.west);
				\draw[->] (others-int.east)  to node[midway, above, sloped] {\tiny State} (wq-in.west);
				\draw[<->, dotted] (wq-in.east)  to (loop.west);
				\draw[->, dotted] (loop.south) to (policy-cls-out);

@@

				\draw[->] (loop) to node[midway, above, sloped] {\tiny NN} (po-me-1);
				\draw[->] (po-me-1) to node[midway, above, sloped] {\tiny NN} (po-me-2);
				\draw[->] (po-me-2) to node[midway, above, sloped] {\tiny NN} (po-me-3);
				\draw[->] (po-me-3) to [out=-45,in=0,looseness=2] node[midway, above, sloped] {\tiny NN} (loop);
			\end{tikzpicture}}
			\caption{Architecture for generalised RL agent on Netronome hardware.}
		\end{figure}
	\end{column}
	\begin{column}{0.4\linewidth}
		\begin{itemize}
			\item Make decisions \alert{where they must be applied}.
			\item ``Bump-in-the-wire'' use of Netronome SmartNIC.
			\item P4 parsing/forwarding/filtering, offload to microcode for full programmability.
			\begin{itemize}
				\item P4 with offload common.
			\end{itemize}
				\item Solution: \alert{make use of on-device parallelism, externs to implement fast, adaptive data-driven applications}.
		\end{itemize}
	\end{column}
\end{columns}
\end{frame}

>>>>

\documentclass[aspectratio=169,xcolor={dvipsnames}
%,notes=only
%,notes
%,show notes on second screen=right
%,handout
]{beamer}
\usetheme[background=light, numbering=fraction]{metropolis}
\usepackage{appendixnumberbeamer}
\usepackage{pgfpages}

@@

\usepackage{lipsum}
%\usepackage[basic]{complexity}
\usepackage[super,negative]{nth}

@@

%bib
\usepackage[maxnames=3,maxbibnames=99,mincrossrefs=5,sortcites
%,backend=bibtex
,style=authortitle
]{biblatex}
\addbibresource{../paper/papers-off.bib}
\addbibresource{../paper/confs-off.bib}

@@

\title{Towards In-Switch Reinforcement Learning}
\author{\vspace{-1em}\textbf{Kyle A. Simpson}\\
	\faEnvelopeO{} \href{mailto:k.simpson.1@research.gla.ac.uk}{\nolinkurl{k.simpson.1@research.gla.ac.uk}}\\
	\vspace{1em}\small{\faGithub{} \href{https://github.com/felixmcfelix}{FelixMcFelix} \hspace{0.5em} \faGlobe{} \url{https://mcfelix.me}}}
\institute{University of Glasgow}
\date{\nth{2} December, 2020}

@@

\begin{frame}{Why programmable data-planes?}
	\begin{columns}
		\begin{column}{0.6\linewidth}
			\begin{figure}
				\resizebox{\linewidth}{!}{
					\begin{tikzpicture}
						\node (iLabel) {Theory};

@@

									\draw[dotted, ->, bend left = 30] (state) -- (agent) node[midway, above] {$t_1$};
									\draw[->] (agent) -- (action) node[midway, right] {$t_2$};
									\draw[dotted, ->] (action) -- (state') node[midway, below] {$t_3$};
						\end{tikzpicture}}};
					\end{tikzpicture}
				}
				\caption{Asynchronous RL delays and state slippage (policy updates omitted).}
			\end{figure}
		\end{column}
		\begin{column}{0.4\linewidth}
			\begin{itemize}
				\item In data-driven, want to \alert{minimise time to act}.
				\item RL assumes that action \& policy update are zero-cost.
				\vspace{-1em}
				\begin{itemize}
					\item Not so in real deployments!
					\item State drift, etc.
				\end{itemize}
				\item Controller contact time, serialisation, ...
				\item In other ML, often need line rate inference.
				\item Programmable network hardware fills this niche.
			\end{itemize}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}{Recent Programmable Trends in Data-Driven Networks}
	\begin{columns}
		\begin{column}{0.6\linewidth}
			\begin{itemize}
				\item ML acceleration, line-rate packet classification.
				\item How? Train model off-NIC, convert to \alert{binary neural network}\footnotemark, or \alert{decision tree}\footnotemark.
				\item Limits? No online training, cost of backprop algo (expensive!), vast data needs.
				\item \alert{What if we need online learning?}
			\end{itemize}
		\end{column}
		\begin{column}{0.4\linewidth}
			\centering
			\resizebox{0.6\linewidth}{!}{
				\includegraphics{images/smartnic.png}
			}

			\resizebox{0.5\linewidth}{!}{
				\includegraphics{images/nn}
			}
		\end{column}
	\end{columns}
\setcounter{footnote}{1}
\footcitetext{DBLP:journals/corr/abs-2009-02353}
\setcounter{footnote}{2}
\footcitetext{DBLP:conf/hotnets/XiongZ19}
\end{frame}

\begin{frame}{Case study: DDoS Prevention}
	\begin{columns}
		\begin{column}{0.4\linewidth}
			\begin{figure}
				\centering
				\resizebox{\linewidth}{!}{
					\begin{tikzpicture}[
					texts/.style = {text=black},
					labeltexts/.style = {text=gray},
					treeline/.style = {draw=uofgburgundy},
					treenode/.style = {texts, circle, centered, fill=white, treeline},
					load/.style = {fill=uofgcobalt},
					loadline/.style = {draw=uofgcobalt, line width=0.75mm},
					loadhide/.style = {fill=uofgcobalt!40!white},
					external/.style = {fill=uofgrust},
					externalhide/.style = {fill=uofgrust!40!white},
					hideline/.style = {draw=uofgsandstone!40!white},
					hidenode/.style = {treenode, hideline},
					grow'=right
					]
					\node [treenode, loadhide, label={[texts]above:Agent 1}] (mainagent) {};
					\node [treenode, loadhide, right = of mainagent] (inner0) {};
					\node [treenode, loadhide, above right = 0.2cm and 1cm of inner0] (inner1) {};
					\node [hidenode, below right = 0.2cm and 1cm of inner0] (inner2) {};
					\node [treenode, loadhide, below right = 0.2cm and 1cm of inner1] (inner3) {};
					\node [treenode, loadhide, right = of inner3] (inner4) {};
					\node [treenode, loadhide, above right = 0.2cm and 1cm of inner4, label={[texts]above:$s_0$}] (s0) {};
					\node [hidenode, below right = 0.2cm and 1cm of inner4, label={[labeltexts]above:$s_1$}] (s1) {};

					\end{tikzpicture}
				}
			\caption{`Global' state for any flow (\textbf{bold} means used by policy).}
			\end{figure}
		\end{column}
		\begin{column}{0.6\linewidth}
			\begin{itemize}
				\item Prior work\footnotemark.
				\item Monitor flow statistics at ingress/egress points.
				\item Use load measurements from flow paths as global state.
				\item OUTPUT: throttle individual flows.
				\item Classical RL.
				\begin{itemize}
					\item Learning time on order of minutes.
				\end{itemize}
			\end{itemize}
		\end{column}
	\end{columns}
\footcitetext{DBLP:journals/tnsm/SimpsonRP20}
\end{frame}

\begin{frame}{Case Study: DDoS Prevention (Architecture)}
	\begin{columns}
		\begin{column}{0.3\linewidth}
			\begin{itemize}
				\item Reward measurements come from network.
				\item Input state mixes local flow data with global load data.
				\item Flow measurements combined, decisions scheduled to prevent overload.
			\end{itemize}
		\end{column}
		\begin{column}{0.7\linewidth}
			\begin{figure}
				\centering
				\resizebox{0.7\linewidth}{!}{\begin{tikzpicture}[scale=1, every node/.style={scale=0.7}]
					\node(remote){Remote};

@@

					\draw[thick, ->] (avfsa.east) to [out=0, in=45] (avfrl.north);
					\node[right=0.3] at (avfsa.east) {\tiny Experience};
					\end{tikzpicture}}
				\caption{
					(Non-PDP) system architecture for RL-driven DDoS defence.
					\label{fig:sys-arch}
				}
				\vspace{-1em}
			\end{figure}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}{Goals... and Reality}
	\centering
	\begin{tabular}{c c c}
		\toprule
		Goal & Solution & Drawback \\ \midrule
		$\bullet$ On-NIC action compute & \onslide+<2->{\alert<2>{Quantisation}} & \onslide+<2->{\alert<2>{Platform Model}} \\
		$\bullet$ On-NIC learning & \onslide+<3->{\alert<3>{Classical RL}} & \onslide+<3->{\alert<3>{Info capacity}} \\
		$\bullet$ Direct action installation & \onslide+<4->{\alert<4>{Custom actions}} & \onslide+<4->{\alert<4>{No intrinsic support}} \\
		$\bullet$ (Partly) External State, Rewards, & \onslide+<5->{\alert<5>{Independent Module}} & \onslide+<5->{\alert<5>{---}} \\
		and Task Independence & & \\
		$\bullet$ Runtime reconfiguration & \onslide+<6->{\alert<6>{P4 Parser + RTE}} & \onslide+<6->{\alert<6>{---}} \\ \bottomrule
	\end{tabular}
\end{frame}

\begin{frame}{Device classes}
	\begin{columns}
		\begin{column}{0.5\linewidth}
			\alert{SmartNICs (e.g., Netronome)}

			\begin{itemize}[<+->]
				\item Low port density.
				\item Easy to have asynchrony:
				\item SOC-based $\rightarrow$ extra cores off the datapath.
				\item NetFPGA $\rightarrow$ can define extra functional units and interconnect.
			\end{itemize}
		\end{column}
		\begin{column}{0.5\linewidth}
			\alert{Programmable Switches (e.g., Tofino)}

			\begin{itemize}[<+->]
				\item High port density.
				\item No additional compute units. Very close to P4 PSA.
				\item But still more powerful--e.g., Tofino supports MUL operations.
				\item Might be doable... deadline-aware.
			\end{itemize}
		\end{column}
	\end{columns}

	\pause
	\vspace{1em}
	We'll mainly focus on SmartNICs.
\end{frame}

\begin{frame}{Timing: Why not offload to the controller?}
	\begin{columns}
		\begin{column}{0.5\linewidth}
			For SmartNICs, the attached host \emph{is the (closest) controller}.

			\begin{itemize}
				\item PCIe access times $\mathcal{O}(\si{\micro\second})$.\footnotemark
				\item MATs recompiled $\mathcal{O}(\si{\second})$. Many rules $\implies$ batching.
				\item Thrift serde time $\mathcal{O}(\si{\milli\second})$.
			\end{itemize}

			%	?? https://github.com/rpclib/benchmarks/blob/master/plots/get_blob_real_log.svg

			\alert{Meanwhile core-to-core on chip around \SI{100}{\nano\second} @ \SI{1.2}{\giga\hertz}.}
		\end{column}
		\begin{column}{0.5\linewidth}
			\begin{figure}
				\includegraphics[width=0.9\linewidth]{../plots/build/rte-timer/rte-times-logx}
				\caption{Netronome rule installation cost \\(1 table, \numrange{1}{65536} rules).}
			\end{figure}
		\end{column}
	\end{columns}

	\footcitetext{DBLP:conf/sigcomm/NeugebauerAZAL018}
\end{frame}

\begin{frame}{Quantisation}
	\begin{columns}
		\begin{column}{0.5\linewidth}
			\begin{figure}
				\includegraphics[width=0.9\linewidth]{../plots/build/marl-quant/accuracy-binary}
				\caption{DDoS throttle accuracy wrt. fixed-point Q$n$.}
			\end{figure}
		\end{column}
		\begin{column}{0.5\linewidth}
			No FPU... so use \alert{Q$n$ fixed-point}.
			\begin{itemize}
				\item For RL updates: need only shift, multiply, add.
				\item \alert{Policy exec only needs add}.
				\item \SI{16}{\bit} fraction has negligible loss.
			\end{itemize}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}{Dynamic Action Installation}
	\begin{itemize}
		\item Netronome w/ P4?
		\begin{itemize}
			\item MAT structure (DCFL) computed on host...
			\item So can't directly interop with P4.
			\item ...But we can have other actions/externs maintain their own lookup tables.
		\end{itemize}
		\item Tofino has features to make this more feasible.
		\begin{itemize}
			\item Action Profiles/Selects
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{Architecting On-NIC RL}
	\begin{columns}
		\begin{column}{0.6\linewidth}
			\begin{figure}
				\resizebox{1\linewidth}{!}{\begin{tikzpicture}
						\node[fill=white!80!uofgcobalt, draw=black, minimum height=5.5cm, minimum width=2.9cm, below right= 0.1 of sw2.north west](p4-master){};
						\node[below right, inner sep=2pt] at (p4-master.north west) {\small P4 Datapath};
						\node[fill=white!90!uofgcobalt, draw, rectangle, rounded corners=0.05cm, below=0.8] (p4-rules) at (p4-master.north) {\begin{varwidth}{2.5 cm}\scriptsize \centering Flow Control Rules\end{varwidth}};
						\node[fill=white!90!uofgcobalt, draw, rectangle, rounded corners=0.05cm, below=0.1] (n1) at (p4-rules.south) {\begin{varwidth}{2.5 cm}\scriptsize \centering Extern-based Action\end{varwidth}};
						\node[fill=white!90!uofgcobalt, draw, rectangle, rounded corners=0.05cm, below=0.1] (n2) at (n1.south) {\begin{varwidth}{2.5 cm}\scriptsize \centering ...\end{varwidth}};
						\node[fill=white!90!uofgcobalt, draw, rectangle, rounded corners=0.05cm, below=0.1] (oswlc) at (n2.south) {\begin{varwidth}{1.5 cm}\scriptsize \centering Control Packet Match\end{varwidth}};
						\node[fill=white!90!uofgcobalt, draw, rectangle, rounded corners=0.05cm, below=0.1] (n3) at (oswlc.south) {\begin{varwidth}{2.5 cm}\scriptsize \centering ...\end{varwidth}};
						\node[fill=white!90!uofgcobalt, draw, rectangle, rounded corners=0.05cm, below=0.1] (n4) at (n3.south) {\begin{varwidth}{2.5 cm}\scriptsize \centering Network Telemetry\end{varwidth}};

						\node (pkt-text) at ($(p4-master.north) + (0.0,0.6)$) {\begin{varwidth}{2.5 cm}\scriptsize \centering Packet In\end{varwidth}};

						\node (pkt-text-out) at ($(p4-master.south) + (0.0,-0.6)$) {\begin{varwidth}{2.5 cm}\scriptsize \centering Packet Out\end{varwidth}};

						\node[fill=white!80!uofgsunshine, draw=black, minimum height=5cm, minimum width=5cm](rli) at ($(p4-master.east) + (5, -1)$){};
						\node[below right, inner sep=2pt] at (rli.north west) (rli-text) {\small RL Island};

						\node[draw=black, dotted, minimum height=1cm, minimum width=2cm](wq-out) at ($(rli-text.south) + (0.5,-0.5)$){};
						\node[below right, inner sep=2pt] at (wq-out.north west) {\small EMEM};
						\node[fill=white!90!uofgsunshine, draw, rectangle, rounded corners=0.05cm, above=0.1] (wq-in) at (wq-out.south) {\begin{varwidth}{2.5 cm}\scriptsize \centering Input Queue\end{varwidth}};

@@

						\node[draw=black, dotted, minimum height=1cm, minimum width=2cm](wq-act) at ($(loop.north) + (0.0,1.5)$){};
						\node[below right, inner sep=2pt] at (wq-act.north west) {\small EMEM};
						\node[fill=white!90!uofgsunshine, draw, rectangle, rounded corners=0.05cm, above=0.1] (wq-actin) at (wq-act.south) {\begin{varwidth}{2.5 cm}\scriptsize \centering Action Queue\end{varwidth}};

@@

						\draw[->] (oswlc.east)  to node[midway, above, sloped] {\tiny Control, Requests} (wq-in.west);
						\draw[->] (n4.east)  to node[midway, above, sloped] {\tiny State} (wq-in.west);
						\draw[<->, dotted] (wq-in.east)  to (loop.west);
						\draw[->, dotted] (loop.south) to (policy-cls-out);

						\draw[->] (loop.north)  to node[midway, above, sloped] {\tiny Actions} (wq-actin.south);

						\draw[->] (wq-actin.west)  to node[midway, above, sloped] {\tiny Actions} (n1.east);

@@

						\draw[->] (pkt-text)  to  (p4-master.north);
						\draw[->] (p4-master.south)  to  (pkt-text-out);

						\draw[->] (loop) to node[midway, above, sloped] {\tiny NN} (po-me-1);
						\draw[->] (po-me-1) to node[midway, above, sloped] {\tiny NN} (po-me-2);
						\draw[->] (po-me-2) to node[midway, above, sloped] {\tiny NN} (po-me-3);
						\draw[->] (po-me-3) to [out=-45,in=0,looseness=2] node[midway, above, sloped] {\tiny NN} (loop);
				\end{tikzpicture}}
				\caption{Architecture for generalised RL agent on Netronome hardware.}
			\end{figure}
		\end{column}
		\begin{column}{0.4\linewidth}
			\begin{itemize}
				\item Classical RL built on tile-coding---\alert{online}.
				\item Async wrt. datapath.
				\item Dynamic selection of last reward, trace info.
				\item \alert{Runtime configurable} (policy, size, application) from data/control-plane.
				\item \alert{Task independent.}
			\end{itemize}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}{How could this (hypothetically) fit the case study?}
	\begin{itemize}
		\item P4 action to gather state on collected flows.
		\begin{itemize}
			\item Flow telemetry in P4 well-documented.
			\item Pass in/schedule state vectors every $\delta{}t$.
		\end{itemize}
		\item Directly pass reward measurements to RL core.
		\item Base policy installed by controller, updated live.
		\item Matched packets poll actions from RL core.
		\begin{itemize}
			\item Map RL actions to state machine, maintain throttling hash table.
			\item Every $\delta{}t'$, batch actions to controller.
		\end{itemize}
	\end{itemize}
\end{frame}

%\begin{frame}{What about higher port-density devices?}
%	content...
%\end{frame}

\begin{frame}{Execution costs (Q15.16)}
	\begin{columns}
		\begin{column}{0.4\linewidth}
			\begin{itemize}
				\item Single-threaded---still to be accelerated.
				\item Small? One tiling per memory tier.
				\item Versus use-case: \SI{330}{\micro\second} on commodity i7.
			\end{itemize}
		\end{column}
		\begin{column}{0.6\linewidth}
			\centering
			\begin{tabular}{ l c c }
				\toprule
				Policy Size & Action (\si{\micro\second}) & Plus Update (\si{\micro\second}) \\ \midrule
				Small & \num{10.66} & \num{14.60} \\
				Max (DDoS) & \num{512.67} & \num{612.55} \\ \bottomrule
			\end{tabular}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}[standout]
	\begin{itemize}
		\item Online in-NIC RL is possible!
		\item In-switch? Less so.
		\item Arch-specific, but similar design for similar hardware class.
		\item Work-in-progress: end-to-end timing, training accuracy, other use-cases, optimisation.
	\end{itemize}
	\alert{Questions?}
\end{frame}
